Eye in a Disk: eyeIntegration human pan-eye and body transcriptome database version 1.00

### 2019-02-25 manuscript.Rmd
starting to write last sections

# Organoid retina differential gene expression versus fetal tissue identifies sets of genes relating to patterning (HOXB family), cell adhesion (protocadherin family), and retinal ganglion function (BRN3/POU4F, NEFL, GAP43, SNCG)

While organoid and retina tissues are highly similar at a pan-transcriptome level, differential expression analysis between organoid and fetal retina reveals differences in related groups of genes.

@@

# Acknowledgements

>>>>

## Organoid retina differential gene expression versus fetal tissue identifies sets of genes relating to patterning (HOXB family), cell adhesion (protocadherin family), and retinal ganglion function (BRN3/POU4F, NEFL, GAP43, SNCG)

While organoid and retina tissues are highly similar at a pan-transcriptome level, differential expression analysis between organoid and fetal retina reveals differences in related groups of genes. Analysis of broad trends in GO term enrichment between differentially expressed genes shows that the HOXB family and protocadherins are differentially expressed between fetal retina and organoids. We noticed that several BRN3/POU4F genes were also differentially regulated

@@

```{r GOterm_fetal_retina_organoid, echo = F, results='asis', warning = F, fig.cap = GOterm_cap, fig.pos = 'H'}
GOterm_cap <- supTab_cap(name='GOterm_fetal_retina_organoid', caption = 'Top GO terms enriched between fetal retina and organoid retina, after paring of redundant terms with REVIGO')
# Output <div>
cat("<div id=\"tbl:GOterm_fetal_retina_organoid\">")
gene_pool_2019 %>% tbl('all_vs_all_GO') %>% filter(Set == 'Retina_Fetal.Tissue-Retina_3D.Organoid.Stem.Cell', ONTOLOGY == 'BP') %>% as_tibble() %>% mutate(qvalue = as.numeric(qvalue)) %>% arrange(qvalue) %>% filter(ID %in% c('GO:0001503','GO:0031589','GO:0050878','GO:0061448','GO:0050678','GO:0030335','GO:0030198', 'GO:0007156', 'GO:0050769', 'GO:0030099')) %>% mutate(geneID = gsub('<br>', ' ', geneID)) %>% as_tibble() %>% regulartable() %>% 
  flextable::align(align='center') %>% 
  font(fontname = 'Linux Libertine O', part = 'all')
#Output Caption (* * for italics)
cat(paste0("\n*",GOterm_cap,"*\n"))
# Output </div>
cat("</div>")
```
# Acknowledgements
